---
title: "Add Code Eligibility Coding Exercise"
format: html
editor: visual
---

## Instructions

Run the following code chunks and complete all necessary prompts with your own code. Once finished, follow the submission instructions on the Github Repository's README.

## Setup

```{r load-packages}
library(tidyverse)
library(palmerpenguins)
library(ggplot2)
library(dplyr)
library(janitor) #added this by my own preference
library(stringr)#for better cpations
```

## Data Exploration

Run the following code cell to explore the data a bit.

```{r data-exploration}


# Create palmer penguins dataframe
penguins_df <- penguins
# Examine the structure of the dataset
str(penguins_df)
glimpse(penguins_df)

# Generate summary statistics
summary(penguins_df)

```

## Data Cleaning

Complete the following data cleaning steps in the `penguins_df` dataframe:

1.  Remove observations with missing values
2.  Create a new column in `penguins_df`called `length_mass` that measures the length to mass ratio of each penguin.

```{r data-cleaning}

# Remove missing values
penguins_df_clean <- penguins_df |>
  clean_names()|>
  drop_na()
#now has 333 observations instead of 344

# Create length_mass column that measures length to mass ratio for each penguin

#using flipper length
penguins_df_length_mass <- penguins_df_clean |>
  mutate(length_mass = flipper_length_mm / body_mass_g)
```

## Data Visualization

Use `ggplot` to make a visualization of your choice with the penguin data. Be sure you include the following in your visualization:

-   An updated title

-   Updated axis labels

-   A color palette/ colors of your choosing (not default ggplot colors)

-   Comments!

```{r data-viz}

flip_mass_sex_graph <- ggplot(data = penguins_df_length_mass, 
                              aes(x = sex, y = length_mass, 
                                  fill=sex)) +
  geom_bar(stat = "summary", fun = "mean") +
    scale_fill_brewer(palette = "Dark2") + 
  labs(title = "Flipper Length to Mass Ratio by Sex", 
       x = "Sex", 
       y = "Flipper Length:Body Mass (mm:g)") +

  theme_classic() +
  theme(
    legend.position = "none",
    plot.margin = margin(t = 10, r = 10, b = 10, l = 10)
  )


flip_mass_sex_graph
                                
```

**Comments:** Females tend to have higher flipper length to body mass ratios on average compared to males. The tendency to have longer flippers could be related to sexual dichotomy of swimming.

**Bonus graph!**

Creating a graph showing relationship between bill length and flipper length.

```{r}

#create df with just gentoo penguins
gentoo_df <- penguins_df_clean |>
  filter(species == "Gentoo")

#create a line graph of bill and flipper length
gent_flip_bill <- ggplot(data = gentoo_df, 
                         aes( x= bill_length_mm, y = flipper_length_mm))+
  geom_smooth() + #apply smoothing to show trend 
  theme_classic() +
  labs(title = "Gentoo Bill and Flipper Length", 
       x = "Bill Length (mm)", 
       y = "Flipper Length (mm)")

gent_flip_bill
```

**Comments:** Bill and flipper length seem positively correlated until flipper length reaches \~230mm and levels out as bill length continues to increase. This suggests a maximum bill length of around 230mm for Gentoo penguins.

That's it! Head back to the README on the Github repo for submission instructions.
