---
title: "Add Code Eligibility Coding Exercise"
format: html
editor: visual
---

## Instructions

Run the following code chunks and complete all necessary prompts with your own code.

## Setup

```{r load-packages}
library(tidyverse)
library(palmerpenguins)
library(ggplot2)
library(dplyr)
```

## Data Exploration

Run the following code cell to explore the data a bit.

```{r data-exploration}

# Examine the structure of the dataset
str(penguins)
glimpse(penguins)

# Generate summary statistics
summary(penguins)

```

## Data Cleaning

Complete the following data cleaning steps:

1.  Remove observations with missing values
2.  Create a column called `length_mass` that measures the length to mass ratio of each penguin.

```{r data-cleaning}

# Remove missing values



# Create length_mass column that measures length to mass ratio for each penguin

```

## Data Visualization

Use ggplot to make a visualization of your choice with the penguin data. Be sure you include the following in your visualization:

-   An updated title

-   Updated axis labels

-   A color palette/ colors of your choosing (not default ggplot colors)

```{r data-viz}

```

That's it! Head back to the README on the Github repo for submission instructions.
